manuscript_removed_text

### 2019-09-09 manuscript/manuscript_removed_text.Rmd
Update manuscript_removed_text.Rmd

>>>>

| Database | Variables downloaded | Citation |
|-----------------------|--------------------------------------------|---------------------|
| WorldClim | Mean annual temperature; temperature seasonality; annual temperature range; mean annual precipitation | [@hijmans_very_2005] |
| WorldClim2 | Solar radiation | [@fick_worldclim_2017] |
| Climate Research Unit (CRU) time-series dataset v 4.03 | Cloud cover; annual frost days; annual wet days; potential evapotranspiration | [@harris_updated_2014] |
| Global Aridity Index and Potential Evapotranspiration Climate Database | Aridity; potential evapotranspiration | [@trabucco_global_2018] |
| TerraClimate | Vapour pressure deficit | [@abatzoglou_terraclimate_2018] |

Table: Sources of climate data

| Variable | Latitude | Mean annual temperature | Temperature seasonality | Potential evapotranspiration | MAT*MAP |
|----------|----------|----------|----------|--------------|----------|
| R~auto~ | 0.65 | 0.77 | 0.62 | 0.63 | NA |
| GPP | 0.64 | 0.63 | 0.72 | 0.36 | 0.64 |
| NPP | 0.50 | 0.52 | 0.52 | 0.33 | 0.56 |
| ANPP | 0.45 | 0.46 | 0.42 | 0.28 | 0.48 |
| ANPP~foliage~ | 0.54 | 0.63 | 0.54 | 0.35 | 0.64 |
| ANPP~woody~ ~stem~ | 0.17 | 0.23 | 0.12 | 0.19 | 0.28 |
| BNPP~root~ | 0.33 | 0.26 | 0.23 | 0.36 | 0.35 |
| BNPP~fine~ ~root~ | 0.15 | 0.11 | 0.16 | 0.11 | 0.19 |
| R~root~ | 0.22 | 0.21 | 0.30 | 0.01* | 0.28 |

Table: R^2^ values presented for latitude, three climate variables, and the best multivariate model for each carbon flux. Values marked * are not significant.
